{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-10 Paper_ttbarH_Draft.tex
fixed two small typos

In this paper, we define a set of observables that are linearly dependent on
$\kp$ and $\kpt$ and are thus sensitive to the relative sign of these
couplings. The proposed observables are based on a particular set of
triple product (TP) structures that we extract from the
expression for the differential cross section for $\ppprocess$,
making use of the fact that the $t$ and $\tbar$ decay products
contain spin information and are sensitive to the
nature of the $tH$ coupling, as noted above.
By using spinor techniques we relate the top
and antitop spin vectors to final state particle
momenta and separate the production process from the decay. This
allows for the straightforward identification of the contributions
that are linearly
sensitive to the couplings.
TPs correlations in these
contributions incorporate the $t$ and $\tbar$ spin vectors; starting
with these TPs, we not only recover the observables given in
Refs.~\cite{Ellis,Guadagnoli} but also propose additional possibilities that
have an increased sensitivity to the $tH$ coupling.
In order to establish a hierarchy in the
sensitivity of the TPs under analysis we use simulated events
to investigate three different
types of observables: asymmetries, mean
values and angular distributions. We note that TP correlations have
been used in Ref.~\cite{Valencia1,*Valencia2} in the context of top-quark
production and decay and in Ref.~\cite{Valencia3} in the framework of
anomalous color dipole operators.  \par

@@

Tables~\ref{table7} and
\ref{table6} summarize the results for the TPs $\epsilon_{5,6,7}$.
We see that $\epsilon_5$ gives rise to asymmetries and mean
values that are clearly higher than those obtained for $\epsilon_6$
and $\epsilon_7$. This is in contrast to the TPs $\epsilon_{1,2,3}$,
for which the asymmetries and mean values are comparable among the
TPs
(see Tables
\ref{table1} and \ref{table5}). We also note that the asymmetry for
$\epsilon_5$ is exactly the same as for $\epsilon_1$, as is expected
from Eq.~(\ref{eq29}), since the proportionality factor relating them
is positive definite. Regarding the mean values, we see by comparing
Tables~\ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$
appear to have a higher sensitivity to the pseudoscalar coupling than do
$\epsilon_{5,6,7}$.  \par

>>>>

In this paper, we define a set of observables that are linearly dependent on
$\kp$ and $\kpt$ and are thus sensitive to the relative sign of these
couplings. The proposed observables are based on a particular set of
triple product (TP) structures that we extract from the
expression for the differential cross section for $\ppprocess$,
making use of the fact that the $t$ and $\tbar$ decay products
contain spin information and are sensitive to the
nature of the $tH$ coupling, as noted above.
By using spinor techniques we relate the top
and antitop spin vectors to final state particle
momenta and separate the production process from the decay. This
allows for the straightforward identification of the contributions
that are linearly
sensitive to the couplings.
TP correlations in these
contributions incorporate the $t$ and $\tbar$ spin vectors; starting
with these TPs, we not only recover the observables given in
Refs.~\cite{Ellis,Guadagnoli} but also propose additional possibilities that
have an increased sensitivity to the $tH$ coupling.
In order to establish a hierarchy in the
sensitivity of the TPs under analysis we use simulated events
to investigate three different
types of observables: asymmetries, mean
values and angular distributions. We note that TP correlations have
been used in Ref.~\cite{Valencia1,*Valencia2} in the context of top-quark
production and decay and in Ref.~\cite{Valencia3} in the framework of
anomalous color dipole operators.  \par

@@

Tables~\ref{table7} and
\ref{table6} summarize the results for the TPs $\epsilon_{5,6,7}$.
We see that $\epsilon_5$ gives rise to asymmetries and mean
values that are clearly larger than those obtained for $\epsilon_6$
and $\epsilon_7$. This is in contrast to the TPs $\epsilon_{1,2,3}$,
for which the asymmetries and mean values are comparable among the
TPs
(see Tables
\ref{table1} and \ref{table5}). We also note that the asymmetry for
$\epsilon_5$ is exactly the same as for $\epsilon_1$, as is expected
from Eq.~(\ref{eq29}), since the proportionality factor relating them
is positive definite. Regarding the mean values, we see by comparing
Tables~\ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$
appear to have a higher sensitivity to the pseudoscalar coupling than do
$\epsilon_{5,6,7}$.  \par
